
\documentclass[]{anand-resume}


\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Anand}{Mathew}{ \urlstyle{same}\url{https://anandmathew.github.io/} \\
\href{mailto:anand_mathew@outlook.com}{anand\_mathew@outlook.com} | 780.880.0674
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{minipage}[t]{0.30\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbf{Proficient Languages}\\
Java \textbullet{}   Python \textbullet{} JavaScript \textbullet{} C \\ \\
\textbf{Web}\\
Node.js \textbullet{} Express \textbullet{} React \textbullet{} MongoDB  \\
Jest/Enzyme \textbullet{} TypeScript \textbullet{} webpack \\  Sails.js \textbullet{} CSS \textbullet{} Apache \textbullet{} AWS  \\ \\
\textbf{Mobile} \\
React Native \textbullet{} Swift \textbullet{} Android \\ \\
\textbf{ Other Tools}\\
Git \textbullet{} Linux \textbullet{} Docker \textbullet{} PostgreSQL \\
Jenkins \textbullet{} Vagrant \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}
\descript{Bachelor of Applied Science, Computer Engineering}
\location{Expected Apr 2020}
\sectionsep
Senior member of the University of Waterloo Computer Science Club and Engineers Without Borders \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\textbf{Coursework} \\
Algorithms and Data Structures \\
Operating Systems \\
Compilers \\
Networking \\
Databases \\
Embedded Systems \\
\sectionsep

\textbf{Hackathons} \\
Hack the North 2016 Participant \\
Winner of 2018 IBM's intern \\ hackathon \\




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{IBM}
\descript{| Software Developer (Cognos Analytics) }
\location{Jan 2019 – Apr 2019 | Toronto, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Reduced search time of the flagship mobile app approximately 52\% by implementing a database (in C) that used tree based index search algorithms to better utilize server hardware resources.
\item Developed the app's entire content navigation front end using React Native.
\end{tightemize}
\sectionsep

\runsubsection{IBM}
\descript{| Software Developer (Business Analytics) }
\location{May 2018 – Sep 2018 | Toronto, ON}
\begin{tightemize}\item Designed and created complex JavaScript React components for an UI toolkit which is used by over 12 000 customers.
\item Championed 100\% code coverage and integrated Jest/Enzyme tests into the developmental workflow.
\end{tightemize}
\sectionsep

\runsubsection{OpenText}
\descript{| Software Developer (Enterprise Cloud Management) }
\location{Sep 2017 – Dec 2017 | Waterloo, ON}
\begin{tightemize}\item Refactored the authentication policy using Node.js , Sails.js and Auth0, implementing JSON Web Token authentication to replace existing session authentication (cookies).

\item Developed a feature using Java and PostgreSQL, which allowed 60 000 previously deleted files to be available to 500 users.
\end{tightemize}
\sectionsep

\runsubsection{IBM}
\descript{| Integration Engineer (Algorithmics) }
\location{Jan 2017 – Apr 2017 | Toronto, ON}
\begin{tightemize}\item Reverse engineered API calls for a financial business database and consequently used Python extensively to create a CLI that is used internally by over 70 engineers.

\item Automated simulations using Python to show the behaviour of 30 GB of stock options data when manipulated by linear interpolation versus curve fitting via a SVI equation.
\end{tightemize}
\sectionsep

\runsubsection{IBM}
\descript{| Software Developer (IBM Cloud) }
\location{May 2016 – Sep 2016 | Toronto, ON}
\begin{tightemize}\item Worked with React, Node.js/Express and Webpack to create a full-stack generalized feedback feature which is fully integrable with Slack and can be used across all IBM Cloud microservices (currently has 1200 messages per week).

\item Updated all the DevOps modals using React, and shipped these front end features to over 20,000 users all over the world.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Baller: A machine learning system that predicts the outcome of NBA games }\\
\begin{tightemize}\item Used Python, scikit-learn and Keras as well as techniques such as \textbf{SVM classification, linear regression and neural network regression} to predict the win/loss outcome of NBA games with an accuracy of 77\%. The training and testing data was scraped using Python from stats.nba.com.
\end{tightemize}
\sectionsep

\runsubsection{Brevity: An application that summarizes large documents} \\
\begin{tightemize}\item Currently working on a project that uses \textbf{natural language processing (NLP) and distributed computing} to generate summaries for large volumes of text. This utilizes React for the frontend, Java for the backend, MongoDB as the database, Python for the NLP and AWS for server computing.
\end{tightemize}
\sectionsep



\end{minipage} 
\end{document}
